Supplement to Manuscript for MADA Project

### 2023-03-09 code/analysis_code/exploratory_analysis/Codes_for_exploratory_analysis.Rmd
Update to MADA Project

```{r}
# Loading required packages
library(readr)
library(tidyverse)
library(dplyr)
library(survey)
library(naniar)
library(gmodels) #for ch-sq frequency table
library(vcd) # for three way frequency table
library(gtsummary)
library(openxlsx)
library(ggplot2)
library(ggthemes)
```

@@

```{r}
# Reading the cleaned csv file
setwd('/Users/ShiwaniSapkota/Desktop/UGA Semester 2 (Spring 2023) courses/EPID 8060E/Project/Raw Data from NHIS')
data_clean <- readRDS("mammogram_ses_clean.rds")
head(data_clean)

>>>>

```{r}
# Loading required packages
library(readr)
library(tidyverse)
library(dplyr)
library(survey)
library(naniar)
library(gmodels) #for ch-sq frequency table
library(vcd) # for three way frequency table
library(gtsummary)
library(openxlsx)
library(ggplot2)
library(ggthemes)
library(here)
```

@@

```{r}
# Reading the cleaned csv file
data_clean <- readRDS(here("data", "processed_cleaned_data", "mammogram_ses_clean.rds"))
head(data_clean)

### 2023-03-09 code/processing_cleaning_code/Codes_for_cleaning.Rmd
Update to MADA Project

```{r}
library(readr)
library(skimr)
library(tidyverse)
library(dplyr)
library(survey)
library(naniar)
```

@@

```{r}
# I will be working on rds file so loading and looking at the raw rds data file
setwd('/Users/ShiwaniSapkota/Desktop/UGA Semester 2 (Spring 2023) courses/EPID 8060E/Project/Raw Data from NHIS')
data_main <- readRDS("mammogram_ses1.rds")
```

@@

```{r}
# Commenting this out so that it does not get created many times
# data_main_clean <- subset(data_main_df, select = c("year", "strata", "psu", "perweight", "sampweight", "sex", "age", "hispanic_status", "income", "education", "marital_status", "region_residence", "insurance_status", "privateinsurance_status", "medicaid_status", "medicare_status", "health_status", "mammogram_status", "cancer_status", "usual_medicalcare_status", "smoking_status", "alcohol_status", "diabetes_status"))
# write_csv(data_main_clean, "mammogram_ses_clean.csv")
# saveRDS(data_main_clean, "mammogram_ses_clean.rds")
```

>>>>

```{r}
library(readr)
library(skimr)
library(tidyverse)
library(dplyr)
library(survey)
library(naniar)
library(here)
```

@@

```{r}
# I will be working on rds file so loading and looking at the raw rds data file
data_main <- readRDS(here("data", "raw_data", "mammogram_ses1.rds"))
```

@@

```{r}
# Commenting this out so that it does not get created many times
# data_main_clean <- subset(data_main_df, select = c("year", "strata", "psu", "perweight", "sampweight", "sex", "age", "hispanic_status", "income", "education", "marital_status", "region_residence", "insurance_status", "privateinsurance_status", "medicaid_status", "medicare_status", "health_status", "mammogram_status", "cancer_status", "usual_medicalcare_status", "smoking_status", "alcohol_status", "diabetes_status"))
# write_csv(data_main_clean, file = (here("data", "processed_cleaned_data", "mammogram_ses_clean.csv"))
# saveRDS(data_main_clean, file = (here("data", "processed_cleaned_data", "mammogram_ses_clean.rds")
```

### 2023-03-09 products/supplement/Supplementary_Material.qmd
Update to MADA Project

# Preparing and loading the raw data file and saving as .csv and .rds files
# setwd('/Users/ShiwaniSapkota/Desktop/UGA Semester 2 (Spring 2023) courses/EPID 8060E/Project/Raw Data from NHIS')
# ddi <- read_ipums_ddi("nhis_00003.xml")
# data <- read_ipums_micro(ddi)

# Saving the raw data file as .csv file and commenting out this code so it does not get created everytime we run this code chunk
# readr::write_csv(data, mammogram_ses.csv")

>>>>

# Preparing and loading the raw data file and saving as .csv and .rds files
# ddi <- read_ipums_ddi("nhis_00003.xml")
# data <- read_ipums_micro(ddi)

# Saving the raw data file as .csv file and commenting out this code so it does not get created everytime we run this code chunk
# readr::write_csv(data, "mammogram_ses.csv")
